Learning Network Size while Training with ShrinkNets

### 2018-01-29 paper/ICML/paper.tex
First attempt implementing the Smooth Filter

\begin{icmlauthorlist}
\icmlauthor{Guillaume Leclerc}{mit}
\icmlauthor{Raul Castro Fernandez}{mit}
\icmlauthor{Manasi Vartak}{mit}
\icmlauthor{Martin Jaggi}{epfl}
\icmlauthor{Samuel Madden}{mit}
\end{icmlauthorlist}

@@

\begin{figure}
\begin{center}
\includegraphics[height=0.97\columnwidth]{regressions}
\vspace*{-5mm}
\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression. From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}

@@

In our previous experiment, we showed that the ShrinkNet loss was
reasonable in practice, we are now interested in the impact on
early pruning. The two most important questions to answer are:
What are the impact on convergence speed (i.e. the number of iterations) ?
and: What is the difference in loss with and without early pruning ?

>>>>

\begin{icmlauthorlist}
\icmlauthor{Guillaume Leclerc}{mit,epfl}
\icmlauthor{Raul Castro Fernandez}{mit}
\icmlauthor{Manasi Vartak}{mit}
\icmlauthor{Martin Jaggi}{epfl}
\icmlauthor{Samuel Madden}{mit}
\end{icmlauthorlist}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{regressions}
\vspace*{-5mm}
\caption{\label{sparsity_accuracy}Loss/Sparsity trade off comparison between Group Sparsity and Shrinknet on linear and logistic regression. From top to bottom and left to right we show the results for \texttt{scm1d}, \texttt{oes97}, \texttt{gina\_prior2} and \texttt{gsadd}.}

@@

In our previous experiment, we showed that the ShrinkNet loss was
reasonable in practice, we are now interested in the impact on
early pruning. The method we suggest for early prunning uses a
parameter $\gamma$ that control the aggressiveness of neuron removal
so we will try to evaluate its impact on the final loss achieved by
the model and the cost required to train the model. Our cost model
is simple and hardware independant, we sum the number of input neurons
at each epoch. In theory the cost in time should be asymptotically
linear to this metric. To have a baseline we also train the same model
but without neuron removal. Keep in mind that this is just in order to
have some reference. Indeed, if we were to remove the neurons with small
weights it would deteriorate the loss (and picking the threshould would
be completely arbitrary). Therefore the baseline is evaluated with all neurons.
One could consider it as a "theoretical lower bound" of the best achievable loss.

We picked multiple combinations of dataset and regularization parameters ($\lambda$) and for each we fit with different aggressiveness parameters ($\gamma$). We measure the loss after convergence and the total cost and report the result in \cref{neuron_removal_figure}. In order to reduce the noise in the result, each experiment was performed $30$ times and we display the range arround $\pm$ $1$ standard deviation.

\textbf{TODO: Interpret the results}
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{neuron_removal}
\vspace*{-5mm}
\caption{\label{neuron_removal_figure}Effect of dynamic neuron removal for different $\gamma$. First column is the difference in the final loss in function of the removal factor. We plot theoretical baseline as a reference. Right column is a proxy of the total cost for training the model (i.e. the sum of input neurons at each epoch). Each row is a dataset/$\lambda$ combination. From top to bottom we have: \texttt{scm1d}/$0.1$, \texttt{oes97}/$0.1$}
